---
title: "Predicti rating and trust on Epinions and Ciao"
author: "Vinh Dang"
date: "4 February 2016"
output: html_document
---

We present our method to predict rating and trust of users on two trust networks: [Epinions](www.epinions.com) and [Ciao](http://www.ciao.com/).

We used the datasets provided by Jiliang Tang, Yahoo Research at [his webpage](http://www.jiliang.xyz/trust.html).

# Preparation

First of all, please make sure that you have installed [R](https://www.r-project.org/). The optional [R Studio](https://www.rstudio.com) is recommended.

Our method required the following packages, so we will install them if needed.

```{r, echo =FALSE}
if (!require(h2o)) {
  install.packages("h2o", repos="http://cran.rstudio.com/")
}

if (!require(R.matlab)) {
  install.packages("R.matlab", repos="http://cran.rstudio.com/")
}

if (!require(lubridate)) {
  install.packages("lubridate", repos="http://cran.rstudio.com/")
}

library (R.matlab)
library (h2o)
library (lubridate)
```

*Note:* If you have problem with installing h2o on Ubuntu, you may refer to [this discussion](http://askubuntu.com/questions/359267/cannot-find-curl-config-in-ubuntu-13-04).

# Experiment

## Predict rating

We will load our code and execute the prediction

```{r, echo=FALSE}
source("Process.R")
```



```{r, echo=FALSE}

```
